Paper notes

### 2019-09-16 paper_notes.Rmd
Add files via upload

i_e = 0.8  # parameters to manipulate
S = 1     # Symmetric single-peaked function: S=1,M=0
M = 0    # Linear + Constant function = S=1,M=1
n = 4     # Schelling Threshold function = S=0,M=1

>>>>

i_e = 0.5  # parameters to manipulate
S = 1     # Symmetric single-peaked function: S=1,M=0
M = 0.5    # Linear + Constant function = S=1,M=1
n = 8     # Schelling Threshold function = S=0,M=1
